Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-04 manuscript/manuscript.tex
Modified manuscript: changes in title and abstract

\begin{summary}
We present a new open-soruce software that computes the gravitational fields
generated by any tesseroid whose density varies arbitrarily in depth, i.e. a
forward gravity model in spherical coordinates for varying densities on the
radial direction.
It is written in Python and Cython language and is compatible with the classes
and functions of the library for geophysical modelling Fatiando a Terra.
It numerically approximates the gravitational fields by applying the
Gauss-Legendre Quadrature along with a preexisting adaptive discretization
algorithm and a new density-based discretization algorithm that control both
the accuracy and the computation time of the forward model.
The first algorithm is regulated by a predefined scalar called distance-size
ratio ($D$) and reduces the errors due to the distance between the tesseroid
and the computation point.
While the second one, controlled by a delta ratio ($\delta$), decreases the
errors introduced by the variation of the density function.
We have also obtained analytical solutions for a spherical shell with variable
density and compared them with the results of the numerical model in case of a
linear, an exponential and a discontinuous density function.
These comparisons allowed to obtain default values for the distance-size and
the delta ratio in order to guarantee the accuracy of the forward model.
The resulting optimal values of $D$ for the gravity potential, the components
of its gradient and the Marussi tensor components are 1, 2 and 8, respectively.
While a $\delta=0.2$ is needed in the computation of every gravity field,
guaranteeing the accuracy even for high varying exponential densities and
discontinuous functions.
We have finally tested the new software by modelling the Neuqu\'en sedimentary
basin, located to the east of the Andes between 32$^\circ$S and 40$^\circ$S
latitude, assigning an exponential density variation to it and computing all
the gravity fields it generates.
\end{summary}

>>>>

\begin{summary}
We present a new methodology to compute the gravitational fields generated by 
any tesseroid whose density varies continuously in depth, i.e. a forward 
gravity model in spherical coordinates for varying densities on the radial 
direction.
It's based on the numerical approximation of the gravitational fields by 
applying the Gauss-Legendre Quadrature along with a preexisting adaptive 
discretization algorithm and a new density-based discretization algorithm that 
control both the accuracy and the computation time of the forward model.
The first algorithm is regulated by a predefined scalar called distance-size 
ratio ($D$) and reduces the errors due to the distance between the tesseroid 
and the computation point.
While the second one, controlled by a delta ratio ($\delta$), decreases the 
errors introduced by the variation of the density function.
We have also obtained analytical solutions for a spherical shell with variable 
density and compared them with the results of the numerical model in case of a 
linear and an exponential density function.
These comparisons allowed to obtain default values for the distance-size and 
the delta ratio in order to guarantee the accuracy of the forward model.
The resulting optimal values of $D$ for the gravity potential, the components 
of its gradient and the Marussi tensor components are 1, 2 and 8, 
respectively.
While a $\delta=0.2$ is needed in the computation of every gravitational 
field, guaranteeing the accuracy even for high varying exponential densities.
We have finally tested the new software by modelling the Neuqu\'en sedimentary 
basin, located to the east of the Andes between 32$^\circ$S and 40$^\circ$S 
latitude, assigning an exponential density variation to it and computing all 
the gravity fields it generates.
\end{summary}
